Examining background gene lists using simulation - comparison of different enrichment techniques

### 2024-09-14 analysis/sim/run_simpw.Rmd
use data if saved
aspect ratio

@@

png("fig3_sim.png", width=7,height=5,units="in",res=150,pointsize=12)
par(mar=c(c(5.1, 5.1, 2.1, 2.1) ))
par(mfrow=c(1,3))

@@

pdf("fig3_sim.pdf", width=7,height=5,pointsize=12)
par(mar=c(c(5.1, 5.1, 2.1, 2.1) ))
par(mfrow=c(1,3))

@@

png("fig3_bars.png", width=7,height=5,units="in",res=150,pointsize=12)
par(mar=c(c(9.1, 3.5, 2.1, 1.1) ))
par(mfrow=c(1,3))
barplot(prec,ylim=c(0,1.1),las=2,main="precision",ylab="")
text((1:6*1.18)-0.45,prec+0.02,labels=signif(prec,3))
barplot(rec,ylim=c(0,1.1),las=2,main="recall",ylab="")
text((1:6*1.18)-0.45,rec+0.02,labels=signif(rec,3))
barplot(f1,ylim=c(0,1.1),las=2,main="F1",ylab="")
text((1:6*1.18)-0.45,f1+0.02,labels=signif(f1,3))
dev.off()

#################################
pdf("fig3_bars.pdf", width=7,height=5,pointsize=12)
par(mar=c(c(9.1, 3.5, 2.1, 1.1) ))
par(mfrow=c(1,3))
barplot(prec,ylim=c(0,1.1),las=2,main="precision",ylab="")
text((1:6*1.18)-0.45,prec+0.02,labels=signif(prec,3))
barplot(rec,ylim=c(0,1.1),las=2,main="recall",ylab="")
text((1:6*1.18)-0.45,rec+0.02,labels=signif(rec,3))
barplot(f1,ylim=c(0,1.1),las=2,main="F1",ylab="")
text((1:6*1.18)-0.45,f1+0.02,labels=signif(f1,3))
dev.off()

@@

png("fig3_box.png", width=7,height=5,units="in",res=150,pointsize=12)
par(mar=c(c(9.1, 3.5, 2.1, 1.1) ))
par(mfrow=c(1,3))
boxplot(prec,cex=0,main="precision",ylab="",col="white",las=2)
beeswarm(prec,add=TRUE,col="darkgray",pch=19)
beeswarm(lapply(prec,mean),add=TRUE,col="black",pch="x",cex=1.0)
boxplot(rec,cex=0,main="recall",ylab="",col="white",las=2)
beeswarm(rec,add=TRUE,col="darkgray",pch=19)
beeswarm(lapply(rec,mean),add=TRUE,col="black",pch="x",cex=1.0)
boxplot(f1,cex=0,main="F1 index",ylab="",col="white",las=2)
beeswarm(f1,add=TRUE,col="darkgray",pch=19)
beeswarm(lapply(f1,mean),add=TRUE,col="black",pch="x",cex=1.0)
dev.off()

pdf("fig3_box.pdf", width=7,height=5,pointsize=12)
par(mar=c(c(9.1, 3.5, 2.1, 1.1) ))
par(mfrow=c(1,3))
boxplot(prec,cex=0,main="precision",ylab="",col="white",las=2)
beeswarm(prec,add=TRUE,col="darkgray",pch=19)
beeswarm(lapply(prec,mean),add=TRUE,col="black",pch="x",cex=1.0)
boxplot(rec,cex=0,main="recall",ylab="",col="white",las=2)
beeswarm(rec,add=TRUE,col="darkgray",pch=19)
beeswarm(lapply(rec,mean),add=TRUE,col="black",pch="x",cex=1.0)
boxplot(f1,cex=0,main="F1 index",ylab="",col="white",las=2)
beeswarm(f1,add=TRUE,col="darkgray",pch=19)
beeswarm(lapply(f1,mean),add=TRUE,col="black",pch="x",cex=1.0)
dev.off()

>>>>

if (file.exists("res.Rds") ) {

  res <- readRDS("res.Rds")

} else {

@@

png("fig3_sim.png", width=8,height=4,units="in",res=150,pointsize=12)
par(mar=c(c(5.1, 5.1, 2.1, 2.1) ))
par(mfrow=c(1,3))

@@

pdf("fig3_sim.pdf", width=8,height=4,pointsize=12)
par(mar=c(c(5.1, 5.1, 2.1, 2.1) ))
par(mfrow=c(1,3))

@@

png("fig3_bars.png", width=8,height=4,units="in",res=150,pointsize=12)
par(mar=c(c(9.1, 3.5, 2.1, 1.1) ))
par(mfrow=c(1,3))
barplot(prec,ylim=c(0,1.1),las=2,main="precision",ylab="")
text((1:6*1.18)-0.45,prec+0.02,labels=signif(prec,3))
barplot(rec,ylim=c(0,1.1),las=2,main="recall",ylab="")
text((1:6*1.18)-0.45,rec+0.02,labels=signif(rec,3))
barplot(f1,ylim=c(0,1.1),las=2,main="F1",ylab="")
text((1:6*1.18)-0.45,f1+0.02,labels=signif(f1,3))
dev.off()

#################################
pdf("fig3_bars.pdf", width=8,height=4,pointsize=12)
par(mar=c(c(9.1, 3.5, 2.1, 1.1) ))
par(mfrow=c(1,3))
barplot(prec,ylim=c(0,1.1),las=2,main="precision",ylab="")
text((1:6*1.18)-0.45,prec+0.02,labels=signif(prec,3))
barplot(rec,ylim=c(0,1.1),las=2,main="recall",ylab="")
text((1:6*1.18)-0.45,rec+0.02,labels=signif(rec,3))
barplot(f1,ylim=c(0,1.1),las=2,main="F1",ylab="")
text((1:6*1.18)-0.45,f1+0.02,labels=signif(f1,3))
dev.off()

@@

png("fig3_box.png", width=8,height=4,units="in",res=150,pointsize=12)
par(mar=c(c(9.1, 3.5, 2.1, 1.1) ))
par(mfrow=c(1,3))
boxplot(prec,cex=0,main="precision",ylab="",col="white",las=2)
beeswarm(prec,add=TRUE,col="darkgray",pch=19)
beeswarm(lapply(prec,mean),add=TRUE,col="black",pch="x",cex=1.0)
boxplot(rec,cex=0,main="recall",ylab="",col="white",las=2)
beeswarm(rec,add=TRUE,col="darkgray",pch=19)
beeswarm(lapply(rec,mean),add=TRUE,col="black",pch="x",cex=1.0)
boxplot(f1,cex=0,main="F1 index",ylab="",col="white",las=2)
beeswarm(f1,add=TRUE,col="darkgray",pch=19)
beeswarm(lapply(f1,mean),add=TRUE,col="black",pch="x",cex=1.0)
dev.off()

pdf("fig3_box.pdf", width=8,height=4,pointsize=12)
par(mar=c(c(9.1, 3.5, 2.1, 1.1) ))
par(mfrow=c(1,3))
boxplot(prec,cex=0,main="precision",ylab="",col="white",las=2)
beeswarm(prec,add=TRUE,col="darkgray",pch=19)
beeswarm(lapply(prec,mean),add=TRUE,col="black",pch="x",cex=1.0)
boxplot(rec,cex=0,main="recall",ylab="",col="white",las=2)
beeswarm(rec,add=TRUE,col="darkgray",pch=19)
beeswarm(lapply(rec,mean),add=TRUE,col="black",pch="x",cex=1.0)
boxplot(f1,cex=0,main="F1 index",ylab="",col="white",las=2)
beeswarm(f1,add=TRUE,col="darkgray",pch=19)
beeswarm(lapply(f1,mean),add=TRUE,col="black",pch="x",cex=1.0)
dev.off()
